A Study on Common Bug Fix Patterns in Rust

### 2022-11-03 discussion.tex
added Ruxanne as the name
added minor changes

In this work, our pipeline successfully mined 20 cross project bug fix patterns. We introduced these patterns in two groups: 12 general patterns and 8 BC-related patterns. Clippy is able to detect four of the BC-related patterns. To the best of our knowledge, the rest of the patterns cannot be reported by the current linting tools. That is why, we believe our work introduces a new direction for IDE tools to help Rust developers.

In each group, we categorized the bug fix patterns based on the underlying program element. The patterns encompass a wide variety of program elements both in the general and BC-related patterns. This shows that our weighting scheme is acceptably unbiased. Also, the introduced patterns are all cross-project fix patterns. Each fix pattern has been seen at least in three different projects, indicating their commonality.

>>>>

In this work, through Ruxanne we successfully mined 20 cross project bug fix patterns. We introduced these patterns in two groups: 12 general patterns and 8 BC-related patterns. Clippy is able to detect four of the BC-related patterns. To the best of our knowledge, the rest of the patterns cannot be reported by the current linting tools. That is why, we believe our work introduces a new direction for IDE tools to help Rust developers.

In each group, we categorized the bug fix patterns based on the underlying program element. The patterns encompass a wide variety of program elements both in the general and BC-related patterns. This shows that our weighting scheme is acceptably unbiased. Also, the introduced patterns are all cross-project fix patterns. Each fix pattern has been seen at least in three different projects, indicating its commonality.

### 2022-11-03 results.tex
added minor changes

We collected 60583 datapoints for general fix patterns using a server with a Xeon Gold 5120 processor (Q3-2017, 14-core 2.2 to 3.2GHz) and the data collection took around 26 hours to compute both $D_g$ and $D_b$. We used $\epsilon=0.0001$ and $Z=5$ as our DBSCAN parameters and that resulted in 577 clusters. After manual analysis, as described in~\ref{sec:manual_analysis_cluster_selection}, we ended up with 10 general patterns, which we describe in Table~\ref{table:general}. As it is shown in the table, we have separated the patterns based underlying program element (Category column). We have given each pattern a specific ID (ID column) and determined the number of instances manifesting that fix pattern (\# Instances column), as well as the number of projects in which the pattern was seen (\# Project column). Now we provide detailed description for each of these patterns:

@@

We collected 27143 datapoints for borrow-checker related fix patterns. We used $\epsilon=0.001$ and $Z=5$ as our DBSCAN parameters and that resulted in 102 clusters. After manual analysis, as described in~\ref{sec:manual_analysis_cluster_selection}, we ended up with 9 borrow-checker related fix patterns, which we, similar to the previous table, describe in Table~\ref{table:bc}. Here we provide detailed description for each of these patterns:

@@

let displayed_attributes = schema.clone().map(|s| {
    s.displayed_name()
        .iter()
<@\textcolor{red}{--}@>      .map(|s| (*s).to_string())
<@\textcolor{green}{++}@>      .map(|s| s.to_string())
        .collect::<HashSet<String>>()
});
\end{lstlisting}

>>>>

We collected 60583 datapoints for general fix patterns using a server with a Xeon Gold 5120 processor (Q3-2017, 14-core 2.2 to 3.2GHz) and the data collection took around 26 hours to compute both $D_g$ and $D_b$. We used $\epsilon=0.0001$ and $Z=5$ as our DBSCAN parameters and that resulted in 577 clusters. After manual analysis, as described in~\ref{sec:manual_analysis_cluster_selection}, we ended up with 12 general patterns, which we describe in Table~\ref{table:general}. As it is shown in the table, we have separated the patterns based underlying program element (Category column). We have given each pattern a specific ID (ID column) and determined the number of instances manifesting that fix pattern (\# Instances column), as well as the number of projects in which the pattern was seen (\# Project column). Now we provide detailed description for each of these patterns:

@@

We collected 27143 datapoints for borrow-checker related fix patterns. We used $\epsilon=0.001$ and $Z=5$ as our DBSCAN parameters and that resulted in 102 clusters. After manual analysis, as described in~\ref{sec:manual_analysis_cluster_selection}, we ended up with 8 borrow-checker related fix patterns, which we, similar to the previous table, describe in Table~\ref{table:bc}. Here we provide detailed description for each of these patterns:

@@
